---
title: "Fantasy Football 2017"
author: "Stephen York"
date: "November 6, 2017"
output: 
  html_document:
    toc: true
    toc_depth: 2

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Fantasy-Football-Schedule-Analysis")
library(highcharter)
library(reshape2)
library(dplyr)
colors = c("#000040", "#000093", "#0020E9", "#0076FF", "#00B8C2", "#04E466", "#49FB25", "#E7FD09", "#FEEA02", "#FFC200", "#FF8500", "#FF3300")
colors <- c("#C3674D", "#B17535", "#94842D", "#6F8F3D", "#46965E", "#0F9883", "#1497A3", "#5890B7", "#9184B6", "#BE75A3", "#D76C83", "#DB705F")

colors <- RColorBrewer::brewer.pal(12, "Paired")


```

```{r load data, include=FALSE}
data <- openxlsx::read.xlsx("FF.xlsx", sheet = 1)
createSchedule <- function(x, y){
  teams <- y
  teams <- as.character(teams[teams != x])
  
  possibleTeams <- teams
  schedule <- data.frame(week = c(1:11), player = NA, result = NA)
  for(i in c(1:11)){
    week <- i
    matchup <- sample(possibleTeams, 1)
    schedule$player[i] <- matchup
    weekNum <- paste0("week", i)
    xScore <- data[,weekNum][data$team == x] #Change week1 to corresponding week in iteration.
    yScore <- data[,weekNum][data$team == matchup]
    if (xScore > yScore){
      result <- "w"
    }else{
      result <- "l"
    }
    schedule$result[i] <- result
    possibleTeams <- possibleTeams[possibleTeams != matchup]
  }
  return(schedule)
}

```


```{r score table, echo=FALSE}

dat <- data 
colnames(dat) <- c("Team", "Week 1", "Week 2", "Week 3",
                   "Week 4", "Week 5", "Week 6", "Week 7",
                   "Week 8", "Week 9", "Week 10", "Week 11")
knitr::kable(dat) 
```

##Score Comparison
```{r score comparison, echo=FALSE, warning = FALSE}

df <- data
colnames(df) <- c("team", "Week 1", "Week 2", "Week 3",
                   "Week 4", "Week 5", "Week 6", "Week 7",
                   "Week 8", "Week 9", "Week 10", "Week 11")

mdata <- melt(df, id.vars = "team")
teams <- unique(mdata$team)
for (p in teams){
  filtDat <- filter(mdata, team == p)
  assign(x = p, value = filtDat)
}

highchart() %>%
  hc_add_series("line", data = Alex, hcaes(x = variable, y = value, group = team))%>%
  hc_add_series("line", data = Neil, hcaes(x = variable, y = value, group = team))%>%
  hc_add_series("line", data = Stephen, hcaes(x = variable, y = value, group = team), visible = FALSE)%>%
  hc_add_series("line", data = Tommy, hcaes(x = variable, y = value, group = team), visible = FALSE)%>%
  hc_add_series("line", data = Leigh, hcaes(x = variable, y = value, group = team), visible = FALSE)%>%
  hc_add_series("line", data = Kyle, hcaes(x = variable, y = value, group = team), visible = FALSE)%>%
  hc_add_series("line", data = Charlie, hcaes(x = variable, y = value, group = team), visible = FALSE)%>%
  hc_add_series("line", data = Kelsey, hcaes(x = variable, y = value, group = team), visible = FALSE)%>%
  hc_add_series("line", data = Sam, hcaes(x = variable, y = value, group = team), visible = FALSE)%>%
  hc_add_series("line", data = Doug, hcaes(x = variable, y = value, group = team), visible = FALSE)%>%
  hc_add_series("line", data = Cooper, hcaes(x = variable, y = value, group = team), visible = FALSE)%>%
  hc_add_series("line", data = Erik, hcaes(x = variable, y = value, group = team), visible = FALSE)%>%
  hc_colors(colors = colors)
  

```

##Average and Standard Deviation
Kudos to Erik for sending me the table.

```{r avg, echo = FALSE}
avgData <- openxlsx::read.xlsx("FF.xlsx", sheet = 3)

knitr::kable(avgData)

```

##Transaction Activity
Transaction activity as of November 24th

```{r transactions, echo=FALSE, warning=FALSE}
transactions <- openxlsx::read.xlsx("FF.xlsx", sheet = 2)
transactions$total <- rowSums(transactions[,c(2,3,5)])
transactions <- arrange(transactions, desc(Acquisitions))

highchart() %>%
  hc_xAxis(categories = transactions$team) %>%
  hc_add_series(data = transactions$Trades, type = "column", name = "Trades") %>%
  hc_add_series(data = transactions$Acquisitions, type = "column", name = "Acquisitions") %>%
  hc_add_series(data = transactions$Activate, type = "column", name = "Activations")%>%
  hc_title(text = "Transactions by Type")

```

##Simulated Schedules
Since the schedule your fantasy team has plays an important role in deciding your team's end of season record, I created a script that will randomly generate 10,000 possible schedules and I then calculated the number of wins a player would recieve in each of those 10,000 schedules using the scores for the respctive weeks since that would be approximately the same no matter who you'd play. The results are displayed for each team in the bar charts below where 'Probability of winning X games' means that of the 10,000 schedules I generated, the team won X number of games that percent of the schedules. The average number of games won is also displayed in the chart.

This isn't an entirely perfect way of looking at things, for example, waiver orders are created using standings, so if you had a different schedule and lost/won more games early in the season then perhaps you'd play the waivers differently which would adjust your scores, but at the very least it, should be an interesting way of looking at things. 

###Alex
####Record this season: 3-8

```{r alex sim, echo=FALSE}

teamName <- "Alex"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[1])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```

###Neil
####Record this season: 6-5

```{r Neil sim, echo=FALSE}

teamName <- "Neil"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[2])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```

###Stephen
####Record this season: 3-8

```{r stephen sim, echo=FALSE}

teamName <- "Stephen"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[3])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```

###Tommy
####Record this season: 6-5

```{r tommy sim, echo=FALSE}

teamName <- "Tommy"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[4])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```

###Leigh
####Record this season: 5-6

```{r leigh sim, echo=FALSE}

teamName <- "Leigh"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[5])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```

###Kyle
####Record this season: 8-3

```{r kyle sim, echo=FALSE}

teamName <- "Kyle"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[6])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```

###Charlie
####Record this season: 5-6

```{r charlie sim, echo=FALSE}

teamName <- "Charlie"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[7])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```

###Kelsey
####Record this season: 7-4

```{r kelsey sim, echo=FALSE}

teamName <- "Kelsey"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[8])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```

###Sam
####Record this season: 7-4

```{r sam sim, echo=FALSE}

teamName <- "Sam"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[9])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```

###Doug
####Record this season: 3-8

```{r doug sim, echo=FALSE}

teamName <- "Doug"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[10])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```

###Cooper
####Record this season: 5-6

```{r cooper sim, echo=FALSE}

teamName <- "Cooper"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[11])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```

###Erik
####Record this season: 8-3

```{r Erik sim, echo=FALSE}

teamName <- "Erik"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[12])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```