---
title: "Fantasy Football 2018, With Perfect Starting Rosters"
author: "Stephen York"
date: "November 20, 2018"
output: 
  html_document:
    toc: true
    toc_depth: 2

---

```{r setup, include=FALSE}
setwd("C:/Fantasy-Football-Schedule-Analysis/2018")
library(highcharter)
library(reshape2)
library(dplyr)
library(formattable)
colors = c("#000040", "#000093", "#0020E9", "#0076FF", "#00B8C2", "#04E466", "#49FB25", "#E7FD09", "#FEEA02", "#FFC200", "#FF8500", "#FF3300")
colors <- c("#C3674D", "#B17535", "#94842D", "#6F8F3D", "#46965E", "#0F9883", "#1497A3", "#5890B7", "#9184B6", "#BE75A3", "#D76C83", "#DB705F")

colors <- RColorBrewer::brewer.pal(12, "Paired")


```

##Intro
So I was curious how well I, as well as everyone else, played their teams in regards to how optimally people chose their starters week-to-week. So, I webscraped ESPN to collect data on which players started and which were left on the bench each week, and from that data, calculated the scores each week had people perfectly set their starting roster. The first few charts and tables below cover some general summary statistics, while at the end I show the results of how teams fair after 10,000 randomly scheduled seasons against other perfectly played teams.

```{r load data, include=FALSE}
data <- openxlsx::read.xlsx("FF 2018.xlsx", sheet = 1)
optimizedData <- openxlsx::read.xlsx("optimizedData.xlsx")

# Function to randomly generate a schedule and determine number of wins.
# x is player schedule is for, y is vector of all possible teams (including x)
createSchedule <- function(x, y){
  teams <- y
  teams <- as.character(teams[teams != x])
  
  possibleTeams <- teams
  schedule <- data.frame(week = c(1:11), player = NA, result = NA)
  for(i in c(1:11)){
    week <- i
    matchup <- sample(possibleTeams, 1)
    schedule$player[i] <- matchup
    weekNum <- paste0("week", i)
    xScore <- data[,weekNum][data$team == x] #Change week1 to corresponding week in iteration.
    yScore <- data[,weekNum][data$team == matchup]
    if (xScore > yScore){
      result <- "w"
    }else{
      result <- "l"
    }
    schedule$result[i] <- result
    possibleTeams <- possibleTeams[possibleTeams != matchup]
  }
  return(schedule)
}

```


##Score Table
This is a table of weekly scores if each team started its perfect roster every single week based on the players it had on its roster at that time. Values that are bolded and in green denote a time where a player actually played their perfect roster. It turns out, it didn't happen very often.  
```{r score table, echo=FALSE, message=FALSE, warning=FALSE}

# find number of times perfect roster occured
#sum(data == optimizedData) - 12 #Subtract 12 because the team names are matches

formattable(optimizedData, list(
  week1 = formatter("span", style = x ~ ifelse(data$week1 == optimizedData$week1, 
                                               style(color = "green", font.weight = "bold"), NA)),
  week2 = formatter("span", style = x ~ ifelse(data$week2 == optimizedData$week2, 
                                               style(color = "green", font.weight = "bold"), NA)),
  week3 = formatter("span", style = x ~ ifelse(data$week3 == optimizedData$week3, 
                                               style(color = "green", font.weight = "bold"), NA)),
  week4 = formatter("span", style = x ~ ifelse(data$week4 == optimizedData$week4, 
                                               style(color = "green", font.weight = "bold"), NA)),
  week5 = formatter("span", style = x ~ ifelse(data$week5 == optimizedData$week5, 
                                               style(color = "green", font.weight = "bold"), NA)),
  week6 = formatter("span", style = x ~ ifelse(data$week6 == optimizedData$week6, 
                                               style(color = "green", font.weight = "bold"), NA)),
  week7 = formatter("span", style = x ~ ifelse(data$week7 == optimizedData$week7, 
                                               style(color = "green", font.weight = "bold"), NA)),
  week8 = formatter("span", style = x ~ ifelse(data$week8 == optimizedData$week8, 
                                               style(color = "green", font.weight = "bold"), NA)),
  week9 = formatter("span", style = x ~ ifelse(data$week9 == optimizedData$week9, 
                                               style(color = "green", font.weight = "bold"), NA)),
  week10 = formatter("span", style = x ~ ifelse(data$week10 == optimizedData$week10, 
                                               style(color = "green", font.weight = "bold"), NA)),
  week11 = formatter("span", style = x ~ ifelse(data$week11 == optimizedData$week11, 
                                               style(color = "green", font.weight = "bold"), NA))
))


```

##Difference
And here is the difference between the potential perfect starting roster and what was actually played.

```{r message=FALSE, warning=FALSE, difference, echo=FALSE}

diff <- optimizedData[,c(2:12)] - data[,c(2:12)]
diff$team <- optimizedData$team
diff <- diff[,c(12, c(1:11))]

formattable(diff, lapply(1:nrow(diff), function(row) {
  area(row, col = -1) ~ color_tile("lightblue", "lightpink")
}))

```

The chart below displays the total points between what potentially could have happened, and what actually happened summed accross all weeks for each player.
```{r message=FALSE, warning=FALSE, graph, echo=FALSE}

totalDiff <- reshape2::melt(diff, id = "team") %>%
  group_by(team) %>%
  summarise(Total = sum(value)) %>%
  arrange(Total)

colnames(totalDiff) <- c("Team", "Total")

  hchart(totalDiff, type = "bar", hcaes(x = Team, y = Total, group = Team),
         pointWidth = 15,
         groupPadding = .5) %>%
  hc_xAxis( type = 'category' ) %>%
    hc_title(text = "Point Difference Between Actual Roster and Perfect Roster, Entire Season")
```

Since its also an interesting stat, here's a table that shows the *percent* of the total points each team got from playing their roster against the hypothetical perfect ones. Think of it as the percent of the total possible points you successfully played accross the entire season.

```{r, percent table, echo = FALSE}

real <- reshape2::melt(data, id = "team") %>%
  group_by(team) %>%
  summarise(sum = sum(value))

perfect <- reshape2::melt(optimizedData, id = "team") %>%
  group_by(team) %>%
  summarise(sum = sum(value))

percent <- round((real$sum/perfect$sum)*100, 2)

percentTable <- data.frame(Team = real$team,
                          Percent = percent)
percentTable <- arrange(percentTable, desc(Percent))

knitr::kable(percentTable, align = "c")

```

##Score Over Time
Using the hypothetical "perfect rosters" each week. Click on names in the legend to select/deslect teams whose score you want to display over time.
```{r score comparison, echo=FALSE, warning = FALSE}

df <- optimizedData

# Rename columns
colnames(df) <- c("team", "Week 1", "Week 2", "Week 3",
                   "Week 4", "Week 5", "Week 6", "Week 7",
                   "Week 8", "Week 9", "Week 10", "Week 11")

# Melt data
mdata <- melt(df, id.vars = "team")

#Extract unique team names
teams <- unique(mdata$team)

# Loop through teams creating individual dataframes that will be their own series in the chart.
for (p in teams){
  filtDat <- filter(mdata, team == p)
  assign(x = p, value = filtDat)
}

highchart() %>%
  hc_add_series("line", data = Alex, hcaes(x = variable, y = value, group = team))%>%
  hc_add_series("line", data = Neil, hcaes(x = variable, y = value, group = team))%>%
  hc_add_series("line", data = Stephen, hcaes(x = variable, y = value, group = team), visible = FALSE)%>%
  hc_add_series("line", data = Tommy, hcaes(x = variable, y = value, group = team), visible = FALSE)%>%
  hc_add_series("line", data = Leigh, hcaes(x = variable, y = value, group = team), visible = FALSE)%>%
  hc_add_series("line", data = Kyle, hcaes(x = variable, y = value, group = team), visible = FALSE)%>%
  hc_add_series("line", data = Charlie, hcaes(x = variable, y = value, group = team), visible = FALSE)%>%
  hc_add_series("line", data = Kelsey, hcaes(x = variable, y = value, group = team), visible = FALSE)%>%
  hc_add_series("line", data = Sam, hcaes(x = variable, y = value, group = team), visible = FALSE)%>%
  hc_add_series("line", data = Doug, hcaes(x = variable, y = value, group = team), visible = FALSE)%>%
  hc_add_series("line", data = Cooper, hcaes(x = variable, y = value, group = team), visible = FALSE)%>%
  hc_add_series("line", data = Erik, hcaes(x = variable, y = value, group = team), visible = FALSE)%>%
  hc_colors(colors = colors)%>%
  hc_xAxis(categories = c(1:11))
  

```

##Average and Standard Deviation
Just some summary statistics using data from our hypothetical perfect teams.
```{r avg, echo = FALSE}
#avgData <- openxlsx::read.xlsx("FF 2018.xlsx", sheet = 3)

avgData <- reshape2::melt(data = optimizedData, id = "team") %>%
  group_by(team) %>%
  summarise(Mean = mean(value),
            Std = sd(value))
colnames(avgData) <- c("Team", "Average Points Scored", "Standard Deviation")

knitr::kable(avgData)

```

##Head-to-Head Scenarios
A matrix of what your team's record would be if you played the same team every week (but assuming you set your starters perfectly). Row is the home team, column is away. Credit to Neil for putting this this one together. 

```{r head-to-head, echo = FALSE}
#FF <- openxlsx::read.xlsx("FF 2018.xlsx", sheet = 1)

FF <- optimizedData

# Create a list to store the name and scores for each week
team <- list(name = NULL, week2= NULL, week3= NULL, week4= NULL, week5= NULL, week6= NULL, week7= NULL, week8= NULL, week9= NULL,
          week10= NULL, week11= NULL)
# This list will contain each team list (contains name and results)
schedules <- list()

# Cry myself to sleep for not having a python dictionary

# Fill out all of the lists
for(i in seq(dim(FF)[2]) ){
  team$name <- FF[i,1]
  team$week1 <- FF[i,2]
  team$week2 <- FF[i,3]
  team$week3 <- FF[i,4]
  team$week4 <- FF[i,5]
  team$week5 <- FF[i,6]
  team$week6 <- FF[i,7]
  team$week7 <- FF[i,8]
  team$week8 <- FF[i,9]
  team$week9 <- FF[i,10]
  team$week10 <- FF[i,11]
  team$week11 <- FF[i,12]
  #Add this shit to the vector of scehdules
  schedules[[i]] <- team
}

# This function takes two team objects determines the win loss record for the "home" team
makeRecord <- function(home, away){
  wins <- 0
  losses <- 0
  
  # this loops through each element name in the team object
  for(element in names(home)){
    if(element != 'name'){
      #Compare the wins and loses between home and away
      if( home[[element]] >= away[[element]]){
        wins <- wins + 1
      } else {
        losses <- losses +  1
      }
    }
  }
  results <- paste(wins, "-",losses)
  return(results)
}

#Loop a bunch to make a matrix of win loss records
df <- FF
names <- as.vector(FF$team)
colnames(df)[1:12] <- names
rownames(df)[1:12] <- names

# Loop through each row
for( rowNumb in seq( dim(df)[1]) ){
  # Loop through each column
  for( colNumb in seq( dim(df)[2]) ){
    df[rowNumb, colNumb] <- makeRecord(schedules[[rowNumb]], schedules[[colNumb]])
  }
}

knitr::kable(df)

```


##Simulated Schedules
Since the schedule your fantasy team has plays an important role in deciding your team's end of season record, I created a script that will randomly generate 10,000 possible schedules and I then calculated the number of wins a player would recieve in each of those 10,000 schedules using the scores for the respctive weeks since that would be approximately the same no matter who you'd play. The results are displayed for each team in the bar charts below where 'Probability of winning X games' means that of the 10,000 schedules I generated, the team won X number of games that percent of the schedules. The average number of games won is also displayed in the chart.

This isn't an entirely perfect way of looking at things, for example, waiver orders are created using standings, so if you had a different schedule and lost/won more games early in the season then perhaps you'd play the waivers differently which would adjust your scores, but at the very least it, should be an interesting way of looking at things. 

###Alex
####Actual Record this season: 8-3

```{r alex sim, echo=FALSE}

#Change the data variable to make things easier...

data <- optimizedData

teamName <- "Alex"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[1])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```

###Neil
####Actual Record this season: 2-9

```{r Neil sim, echo=FALSE}

teamName <- "Neil"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[2])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```

###Stephen
####Actual Record this season: 7-4

```{r stephen sim, echo=FALSE}

teamName <- "Stephen"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[3])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```

###Tommy
####Actual Record this season: 9-2

```{r tommy sim, echo=FALSE}

teamName <- "Tommy"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[4])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```

###Leigh
####Actual Record this season: 5-6

```{r leigh sim, echo=FALSE}

teamName <- "Leigh"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[5])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```

###Kyle
####Actual Record this season: 5-6

```{r kyle sim, echo=FALSE}

teamName <- "Kyle"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[6])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```

###Charlie
####Actual Record this season: 5-6

```{r charlie sim, echo=FALSE}

teamName <- "Charlie"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[7])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```

###Kelsey
####Actual Record this season: 5-6

```{r kelsey sim, echo=FALSE}

teamName <- "Kelsey"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[8])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```

###Sam
####Actual Record this season: 4-7

```{r sam sim, echo=FALSE}

teamName <- "Sam"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[9])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```

###Doug
####Actual Record this season: 7-4

```{r doug sim, echo=FALSE}

teamName <- "Doug"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[10])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```

###Cooper
####Actual Record this season: 4-7

```{r cooper sim, echo=FALSE}

teamName <- "Cooper"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[11])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```

###Erik
####Actual Record this season: 5-6

```{r Erik sim, echo=FALSE}

teamName <- "Erik"

# create empty vector to add to
iterations <- 10000
wins <- rep(NA, iterations)

# Run 10000 simulations
for (i in c(1:iterations)){
  schedule <- createSchedule(teamName, data$team)
  numWins <- length(grep(pattern = "w", schedule$result))
  wins[i] <- numWins
}

# Calculate summary statistics
minWins <- min(wins)
maxWins <- max(wins)
meanWins <- round(mean(wins), 1)

# Create frequency dataframe
wins <- sort(wins)
winDat <- data.frame(iteration = c(1:iterations),
                     wins = wins)
winCount <- dplyr::count(winDat, wins)
winCount$percentage <- round(((winCount$n/iterations) * 100), 1)

# Graph
highchart() %>%
  hc_add_series(data = winCount, "column", hcaes(x = wins, y = percentage), name = "Percent Chance", color = colors[12])%>%
  hc_xAxis(plotLines = list(list(
    value = meanWins, color = "black", width = 1.5,
    label = list(text = paste0("Average # of Wins - ", meanWins)),
    zIndex = 5
  )),
  title = list(text = "Number of Wins")) %>%
  hc_yAxis(labels = list(format = "{value} %")) %>%
  hc_tooltip(
    pointFormat = "Probability of winning {point.x} games: <b>{point.y}</b><br/>",
    valueSuffix = ' %',
    headerFormat = ""
  ) %>%
  hc_title(text = "Number of wins based on 10,000 simulations")


```